Total Platform Cyber Protection

### 2016-08-23 paper.tex
Finished adding Application layer, added a new citation for static info flow analysis

Attempts have been made to measure an application's attack
surface~\cite{howard2003,manadhata2007,manadhata2008,ruprecht2014}.
This has the benefit of attempting to quantify the attack surface of
an application, which in itself is a difficult problem.

Several research works attempt to reduce the attack surface. Some
approaches try to statically analyze for deadcode, then restrict the
execution of the deadcode during runtime~\cite{kurmus2011}. Other ways
attempt to leverage compile-time configurability to reduce the attack
surface~\cite{tartler2012,kurmus2013,ruprecht2014}. A different
approach is to reduce the attack surface by partitioning the
application into different privilege levels~\cite{barth2010,xu2012}.
Other approaches attempt to restrict the communication between
applications, in order to reduce opportunities for the attacker to
input data to the system~\cite{kantola2012}.

@@

Significant progress in this area started with the idea of
control-flow integrity, essentially ensuring dynamically at runtime
that the control-flow of the application does not
deviate~\cite{abadi2005,abadi2009}. The first implementations were
deemed infeasible, so later research attempted to improve the
efficiency of control-flow integrity~\cite{zhang2013,tice2014,bletsch2011,zhang2013,zhang2013a}.

Researchers have advanced the state of attacks against control-flow
hijacking. The most advanced of these is return-oriented programming
(ROP), in which an attacker reuses bits of code from the original
application, so that the attacker can hijack the control-flow of the
application without introducing new code~\cite{roemer2012,bletsch2010,tran2011}. 
Researchers have also improved these ROP
techniques~\cite{checkoway2010,buchanan2008,kayaalp2012,chen2012,goktas2014,schwartz2011}
 and applied them to a different
architecture~\cite{davi2012}.

Other research has looked at defending ROP attacks~\cite{pappas2012,davi2009,davi2011,onarlioglu2010,gupta2013,pappas2012,lu2011,lu2011a,homescu2012,gokta2014,cheng2014,pappas2013,snow2013,hiser2012,wartell2012} or detecting ROP
attacks\cite{polychronakis2011}. Metastudies have looked at the
effectiveness of these defenses~\cite{skowyra2013,schuster2014}.

Finally, other research has shown that even with perfect control-flow
integrity, due to the impreciseness of statically creating the
control-flow graph, an attacker can still hijack the control
flow~\cite{carlini2015,schuster2015,carlini2014,davi2014}.

@@

Other research has looked at preventing access control
vulnerabilities~\cite{dalton09:nemesis}, or statically detecting
them~\cite{sun2011}.
Some research has looked at other types of logic
flaws, such as
Privilege escalation vulnerabilities~\cite{monshizadeh2014}, data disclosure
vulnerabilities~\cite{muthukumaran2015}, single sign-on vulnerabilities~\cite{zhou2014}, and parameter tampering vulnerabilities~\cite{bisht2010,bisht2011}.

Execution After Redirect is another type of logic flaw
vulnerability in web applications~\cite{doupe2011,payet2013}.

Work on detecting logic vulnerabilities directly started with
attempting to infer security specifications of an
application~\cite{tan08:autoises,Livshits2009a}. Other approaches dynamically
execute the application to infer likely invariants, then use static
analysis to attempt to find paths that violate those
invariants~\cite{felmetsger10:logic}. Further work tried to find missing
security (authorization) checks automatically, without prior knowledge
of the checks~\cite{son2011,son2013}.

@@

Research has been made to automatically generate test inputs for Concolic testing (so that all execution paths can be tested) for major languages like C, C++, and Java~\cite{garg2013,jayaraman2009,sen2005}. Other research in this area includes an approach to combine Random testing~\cite{bird1983automatic} with Concolic execution~\cite{majumdar2007}, automated Concolic testing for smartphone applications~\cite{anand2012automated}, and using Concolic testing in a distributed, scalable way~\cite{kim2012scalable}. There has also been some work on discussing concolic testing tools and their limitations~\cite{qu2011}.

There has been significant research in the area of analysis of an application. Dynamic analysis~\cite{ball1999concept} --- one such approach --- analyzes the code at run time, and much research in this area has been into Taint-based tracking~\cite{chang2008}, Anomaly Detection~\cite{cova2007,li11:block,li2012}, Context-sensitive sanitization for popular languages and templating languages~\cite{saxena2011,samuel2011}, Binary Analysis~\cite{song2008}, and Logic vulnerabilities~\cite{felmetsger2010}. Other work has looked at automated attack generation using model checking~\cite{martin08:goal_directed_mc}, and classifying the available countermeasures for the C and C++ languages~\cite{younan2012}.

@@

While a majority of research in this area is concentrated on popular attacks like XSS and SQL Injection, there is also some research on other topics like side-channel leaks~\cite{zhang2010} and information flow analysis~\cite{liu2010static,tripp2009,Livshits2009a}.

@@

Early research was focused on rewriting unsafe instructions and providing interfaces for system calls to restrict program's access~\cite{wahbe1993,mccamant2006}. Native Client (NaCl)~\cite{yee2009} is a sandbox provided by Google that offers x86 untrusted Native code execution in Chrome browser using x86 memory segmentation. Therefore, web developers can leverage the performance of executing native code in a safe environment. Xax~\cite{douceur2008} is another similar technology that is in form of a browser plug-in that provides an abstraction layer for OS system calls. Other research extends this technology by covering ARM and x86-64~\cite{zhao2011,sehr2010,ansel}. Others attempt to reduce the overhead of performing binary rewriting and memory isolation~\cite{ford2008,jana2011}. Sandboxing is also used for executing untrusted native code in Android applications~\cite{sun2014,afonso2016}.

The other approach toward protecting against malicious code is to analyze the code and detect malicious behavior~\cite{zhou2012}. Despite all the efforts that have been made to keep malicious apps off the Android market, malicious apps can still find their way into the app store by bypassing the Google Bouncer~\cite{lockheimer:2012} using different techniques. Bouncer uses sandboxing techniques to run apps in a confined environment, but researchers~\cite{oberheide2012dissecting} have shown that apps can fingerprint Bouncer and the environment in which they are being analyzed, using evasion and obfuscating techniques to complicate the reverse engineering process. If apps could detect that they are being analyzed, they can hold off on running their malicious code while being analyzed. A lot of research has been done to fingerprint the Android analyzers to show that evading detection is possible~\cite{maier2014,jing2014,vidas2014}. Other approaches use analysis to detect logic bombs, i.e., when an application changes its behavior under certain conditions~\cite{fratantonio2016}.

>>>>

Attempts have been made to measure an application's attack
surface~\cite{howard2003, manadhata2007, manadhata2008, ruprecht2014}.
This has the benefit of attempting to quantify the attack surface of
an application, which in itself is a difficult problem.

Several research works attempt to reduce the attack surface. Some
approaches try to statically analyze for deadcode, then restrict the
execution of the deadcode during runtime~\cite{kurmus2011}. Other ways
attempt to leverage compile-time configurability to reduce the attack
surface~\cite{tartler2012, kurmus2013, ruprecht2014}. A different
approach is to reduce the attack surface by partitioning the
application into different privilege levels~\cite{barth2010, xu2012}.
Other approaches attempt to restrict the communication between
applications, in order to reduce opportunities for the attacker to
input data to the system~\cite{kantola2012}.

@@

Significant progress in this area started with the idea of
control-flow integrity, essentially ensuring dynamically at runtime
that the control-flow of the application does not
deviate~\cite{abadi2005, abadi2009}. The first implementations were
deemed infeasible, so later research attempted to improve the
efficiency of control-flow integrity~\cite{zhang2013, tice2014,
	bletsch2011, zhang2013, zhang2013a}.

Researchers have advanced the state of attacks against control-flow
hijacking. The most advanced of these is return-oriented programming
(ROP), in which an attacker reuses bits of code from the original
application, so that the attacker can hijack the control-flow of the
application without introducing new code~\cite{roemer2012,
	bletsch2010, tran2011}. Researchers have also improved these ROP
techniques~\cite{checkoway2010, buchanan2008, kayaalp2012, chen2012,
	goktas2014, schwartz2011} and applied them to a different
architecture~\cite{davi2012}.

Other research has looked at defending ROP attacks~\cite{pappas2012,
	davi2009, davi2011, onarlioglu2010, gupta2013, pappas2012, lu2011,
	lu2011a, homescu2012, gokta2014, cheng2014, pappas2013, snow2013,
	hiser2012, wartell2012} or detecting ROP
attacks\cite{polychronakis2011}. Metastudies have looked at the
effectiveness of these defenses~\cite{skowyra2013, schuster2014}.

Finally, other research has shown that even with perfect control-flow
integrity, due to the impreciseness of statically creating the
control-flow graph, an attacker can still hijack the control
flow~\cite{carlini2015, schuster2015, carlini2014, davi2014}.

@@

Other research has looked at preventing access control
vulnerabilities~\cite{dalton09:nemesis}, or statically detecting
them~\cite{sun2011}.
Some research has looked at other types of logic
flaws, such as
Privilege escalation vulnerabilities~\cite{monshizadeh2014}, data disclosure
vulnerabilities~\cite{muthukumaran2015}, single sign-on vulnerabilities~\cite{zhou2014}, and parameter tampering vulnerabilities~\cite{bisht2010, bisht2011}.

Execution After Redirect is another type of logic flaw
vulnerability in web applications~\cite{doupe2011, payet2013}.

Work on detecting logic vulnerabilities directly started with
attempting to infer security specifications of an
application~\cite{tan08:autoises, Livshits2009a}. Other approaches dynamically
execute the application to infer likely invariants, then use static
analysis to attempt to find paths that violate those
invariants~\cite{felmetsger10:logic}. Further work tried to find missing
security (authorization) checks automatically, without prior knowledge
of the checks~\cite{son2011, son2013}.

@@

Research has been made to automatically generate test inputs for Concolic testing (so that all execution paths can be tested) for major languages like C, C++, and Java~\cite{garg2013, jayaraman2009, sen2005}. Other research in this area includes an approach to combine Random testing~\cite{bird1983automatic} with Concolic execution~\cite{majumdar2007}, automated Concolic testing for smartphone applications~\cite{anand2012automated}, and using Concolic testing in a distributed, scalable way~\cite{kim2012scalable}. There has also been some work on discussing concolic testing tools and their limitations~\cite{qu2011}.

There has been significant research in the area of analysis of an application. Dynamic analysis~\cite{ball1999concept} --- one such approach --- analyzes the code at run time, and much research in this area has been into Taint-based tracking~\cite{chang2008}, Anomaly Detection~\cite{cova2007, li11:block, li2012}, Context-sensitive sanitization for popular languages and templating languages~\cite{saxena2011, samuel2011}, Binary Analysis~\cite{song2008}, and Logic vulnerabilities~\cite{felmetsger2010}. Other work has looked at automated attack generation using model checking~\cite{martin08:goal_directed_mc}, and classifying the available countermeasures for the C and C++ languages~\cite{younan2012}.

@@

While a majority of research in this area is concentrated on popular attacks like XSS and SQL Injection, there is also some research on other topics like side-channel leaks~\cite{zhang2010} and information flow analysis~\cite{liu2010static,tripp2009,livshits2009a}.

@@

Early research was focused on rewriting unsafe instructions and providing interfaces for system calls to restrict program's access~\cite{wahbe1993, mccamant2006}. Native Client (NaCl)~\cite{yee2009} is a sandbox provided by Google that offers x86 untrusted Native code execution in Chrome browser using x86 memory segmentation. Therefore, web developers can leverage the performance of executing native code in a safe environment. Xax~\cite{douceur2008} is another similar technology that is in form of a browser plug-in that provides an abstraction layer for OS system calls. Other research extends this technology by covering ARM and x86-64~\cite{zhao2011, sehr2010, ansel}. Others attempt to reduce the overhead of performing binary rewriting and memory isolation~\cite{ford2008, jana2011}. Sandboxing is also used for executing untrusted native code in Android applications~\cite{sun2014, afonso2016}.

The other approach toward protecting against malicious code is to analyze the code and detect malicious behavior~\cite{zhou2012}. Despite all the efforts that have been made to keep malicious apps off the Android market, malicious apps can still find their way into the app store by bypassing the Google Bouncer~\cite{lockheimer:2012} using different techniques. Bouncer uses sandboxing techniques to run apps in a confined environment, but researchers~\cite{oberheide2012dissecting} have shown that apps can fingerprint Bouncer and the environment in which they are being analyzed, using evasion and obfuscating techniques to complicate the reverse engineering process. If apps could detect that they are being analyzed, they can hold off on running their malicious code while being analyzed. A lot of research has been done to fingerprint the Android analyzers to show that evading detection is possible~\cite{maier2014, jing2014, vidas2014}. Other approaches use analysis to detect logic bombs, i.e., when an application changes its behavior under certain conditions~\cite{fratantonio2016}.
